---
title: "Alcohol vs Seat choice"
author: "Louie A "
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```



## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot
```{r}
# Plotting the notched box plot with red outliers and centered title
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
The guys in the back are drinking 3x the amount of alcohol than the guys in the front. the data shows that min is 0 but there are 4 in the back 1 in the middle and 0 in the front row. there is a huge difference between the back row and the front row with the back rounded to 10, middle 3 and 0 in the front. there are alot of poeple in the middle which does even out the amount of drinkers


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

```{r}
# Load the necessary library
library(stats)

# Perform ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
summary(anova_result)
```

```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)
```





## Conclusions
In summary we conclusion we discovered that those who sat in the back drank more alcohol the those who sat i the middle/ front row. We used a plot code to look at a graph that shows this. we also look at a number graph to see who sat where the most and what is the average drinker per person.  We discovered that most of the people sat in the middle row in which evened out the average drinker. We used multiple graphs with the aid of Chat GPT,  it gave code to look at the number in different ways to test the results out 

